DraftOne

### 2016-06-07 DraftOne.Rmd
Adding functions for exposure data without seasonal trends to package

```{r}
# Function to generate a binary exposure
binary_exposure <- function(n, p_exp, start.date = "2000-01-01", ...){
        start.date <- as.Date(start.date)
        date <- seq(from = start.date, by = 1, length.out = n)
        x <- sample(c(0, 1), size = n, replace = TRUE,
                    prob = c(1-p_exp, p_exp))
        df <- data.frame(date, x)
        return(df)
}
binary_exposure(n = 5, p_exp = 0.25)
```

@@

```{r}
# Function to generate a continuous exposure
continuous_exposure <- function(n, mu, sd, start.date = "2000-01-01", ...){
        start.date <- as.Date(start.date)
        date <- seq(from = start.date, by = 1, length.out = n)
        x <- rnorm(n, mean = mu, sd = sd)
        df <- data.frame(date, x)
        return(df)
}
continuous_exposure(n = 5, mu = 10, sd = 10)
```

>>>>

```{r}
# Function to generate a binary exposure
binary_exposure

binary_exposure(n = 5, p_exp = 0.25)
```

@@

```{r}
# Function to generate a continuous exposure
continuous_exposure

continuous_exposure(n = 5, mu = 10, sd = 10)
```
